\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\usepackage{algpseudocode}
\usepackage{algorithm}
\newtheorem{lemma}[theorem]{Lemma}
\usepackage{listings}

\title{COMP 550 – Algorithms and Analysis}
\author{Spring 2023-Assignment05}
\date{  Issue Date: March 29, 2023 
        $\vspace{0.5cm}$
        \\Due Date: Wednesday, April 5, 11:55 pm
        $\vspace{0.5cm}$
        \\ Marks: 5
        \\
        $\vspace{1cm}$
        \\ Student Name:$\rule[-5pt]{8.2cm}{0.05em}$ 
        $\vspace{1cm}$
        \\ Student PID:$\rule[-5pt]{8.2cm}{0.05em}$ }

\begin{document}

\maketitle
\begin{center}
\textbf{Submission:}
\end{center}
\begin{itemize}
    \item \textbf{You must upload your submission(s) before the deadline in Gradescope.}
    \item \textbf{Please ensure that your answers are within the given space allocated after the question.}
\end{itemize}

$\vspace{0.2cm}$

\begin{center}
\textbf{Rules for ALL HWs}:
\end{center}
You are encouraged to \textit{\underline{\textbf{discuss}}} the homework assignments and study together in groups, but when it comes to formulating/writing solutions \textit{\underline{\textbf{you must work}}} \textit{\underline{\textbf{alone and independently}}}. If required, you should be able to explain your answer clearly to TAs/LAs. Copying homework solutions from another student, from the  Internet, solution sets of friends, or other  sources will be considered cheating and treated accordingly.
\newpage

\section{Minimum Spanning Tree}
\doublespacing
\begin{enumerate}
    \item For each of the following statements decides whether they are correct. If it is incorrect, provide a counter-example. \\
    Assume $G=(V,E)$ is undirected and connected. Do not assume the edge weights are distinct unless specifically stated.
    \begin{enumerate}
        \item let $e$ be any edge of minimum weight in $G$. Then $e$ must be part of some MST.
        \item If $G$ has a cycle with a unique lightest edge $e$, then $e$ must be part of every MST.
        \item For any $r > 0$, define an r-path as a path whose edges all have a weight less than $r$. If $G$ contains an r-path from $s$ to $t$, then every MST of $G$ must also contain an r-path from $s$ to $t$.
    \end{enumerate}
    \newpage
    \
    \\
    \newpage

    \item Consider $G=(V,E)$ is undirected and connected. Prove that If $e$ is part of some MST of $G$, then it must be the lightest edge across some cut of $G$.
    \newpage
    


    \item Is the algorithm correct? If so, prove it. Otherwise, give a counterexample and explain why it doesn’t work.
    \begin{algorithm}
    \caption{FindMST ($G$:graph on $n$ vertices)}\label{alg:cap}
    \begin{algorithmic}
    \If{n=1}  \textbf{return the empty set}
    \EndIf
    \State $T_1 \gets $ FindMST($G1$: subgraph of $G$ induced on vertices $\{ 1,2\dots \frac{n}{2}\}$)
    \State $T_2 \gets $ FindMST($G2$: subgraph of $G$ induced on vertices $\{\frac{n}{2}+1,\dots n\}$)
    \State $e \gets $ cheapest edge across the cut $\{1,2\dots \frac{n}{2}\}$ and $\{\frac{n}{2}+1,\dots n\}$.\\
    \textbf{return $T_1 \cup T_2 \cup \{e\}$}
    \end{algorithmic}
    \end{algorithm}
    \newpage


    
    
\end{enumerate}
    \section{Bellman-Ford}
    \begin{enumerate}
        \item Let $G=(V,E)$ be a \textbf{directed} graph. Under what condition does the Bellman-Ford algorithm return the same shortest path tree (from source $s \in V$) regardless of the ordering on edges? (That is if this condition is satisfied, it is guaranteed that Bellman-Ford will return the same path tree)
    \end{enumerate}

\end{document}